Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-21 chapters/introduction/introduction.tex
finish up

Benefited from the fast growing monitoring satellite and drone markets,
the geo-tagged aerial imagery becomes more publicly accessible
than ever. Aerial imagery downloading services like
Microsoft Bing Map provide aerial images of various
resolutions, which cover most areas of the world with accurate
geographic registration, making aerial imagery a rich source for
reference databases. We refer to geo-calibration
methods which use the aerial imagery for geographic reference as
ground-to-aerial geo-calibration.

@@

\subsection{Geo-Calibration for Feature Learning}
Our methods also focus on lavaging the camera geographic information to
deal with the challenges of lacking manually annotated data during DNN
training. The insight is that the camera geographic information
encodes semantic information because it is related to the
appearances of the scenes.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning:}
  Current machine learning methods address problems that involves mostly
  the ground-level imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the satellite/aerial imagery. In
  \chapref{crosstransf}, we proposed a method to learn the aerial image
  semantic segmentation with only ground-level ground truth. Our method
  exploits the spatial correspondences between images in cross-view
  pairs. 
  In this work, we try to transfer the semantics from the ground
  imagery to the aerial imagery by identifying the latent geometry
  correspondences between these two. Similar to the monocular depth
  estimation methods that driven by the technique called {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the aerial
  images to the ground images, and to segment the aerial images
  jointly.
  \newline

  \item \textbf{Geo-Temporal Feature Learning:}
  In \chapref{whenwhere}, we demonstrate that our algorithm is able to
  learn geo-temporal image representations with geographic locations and
  capture time.
  Our work is most similar to Li and Snavely~\cite{li2018learning},
  who propose an approach for learning intrinsic images by observing
  image sequences with varying illumination over time. While their
  targets are reflectance and shading images of the scene, we consider
  two novel pretext tasks, time and location estimation.
  By learning to predict the geographic location and capture time of
  the query image, our network learns to extract geo-temporal features
  from the image.

>>>>

Benefited from the fast growing monitoring satellite and drone markets,
the geo-tagged aerial imagery becomes more publicly accessible
than ever. Aerial imagery downloading services like
Microsoft Bing Map provide aerial images of various
resolutions, which cover most areas of the world with accurate
geographic registration, making aerial imagery a rich source for
reference databases. We refer to geo-calibration
methods which use the aerial imagery for geographic reference as
ground-to-aerial geo-calibration. Data used for ground-to-aerial
geo-calibration is referred to as cross-view pairs.
A cross-view pair consists of a ground image and an aerial image at
the same location, and but not necessarily aligned in orientation.

@@

\subsection{Geo-Calibration for Feature Learning}
Our methods also provide another way to dealing with the challenges of
lacking manual annotations during DNN training. By learning to
geo-calibrate a camera, we believe the networks are able to learn
high-level image representations. This belief comes from the fact that
the geo-calibration information of a camera encodes semantic
information because it is closely related to the appearances of the
scene.
We explore two types of learning techniques for high-level feature
extraction: 1) semantic segmentation of the aerial imagery with
ground-level annotations which is plentiful, and 2) geo-temporal
features with automatically annotated geographic locations and time.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning:}
  Most current machine learning methods study problems involving the
  ground imagery. There exist many annotated dataset of the ground
  imagery while much fewer of the aerial imagery. 
  In \chapref{crosstransf}, we proposed a
  method to learn to semantically segment aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in cross-view pairs. 
  In this work, we try to transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
  which have been successfully applied in monocular depth estimation,
  our network learns geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  \newline

  \item \textbf{Geo-Temporal Feature Learning:}
  In \chapref{whenwhere}, we demonstrate that our algorithm is able to
  learn geo-temporal image representations with geographic locations and
  capture time which are automatically captured by smart devices.
  Our work is most similar to Li and Snavely~\cite{li2018learning},
  who propose an approach for learning intrinsic images by observing
  image sequences with varying illumination over time. While their
  targets are reflectance and shading images of the scene, we consider
  two novel pretext tasks, time and location estimation.
  By learning to predict the geographic location and capture time of
  the query image, our network learns to extract geo-temporal features
  from the image.
